---
title: "A title for the slides"
subtitle: "A subtitle"
author: "Your Name"
date: May 9, 2018
output: 
  beamer_presentation:
    includes:
      in_header: header.tex
---

```{r include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
knitr::knit_hooks$set(resize = function(before,
                                        options, envir) {
    if (before) {
      return('\\resizebox{\\textwidth}{!}{')
    } else {
      return('}')
    }
})
```

```{r libs}
library(dplyr)
library(knitr)
library(broom)
library(ggplot2)
```

## Summary

- This a an example.
- It shows several slides.
- Some with tables.
- One with a figure.

## Methods

1. Simulate some data.
1. Test for differences using t-test.
1. Idem using a linear regression.

## Data

Here is what the data looks like:

```{r sim}
N = 40
df = tibble(group=rep(1:2,N), var=rnorm(2*N,0,10)) %>% mutate(data=rnorm(n(), group)+var)
df %>% head %>% kable
```


## t-test

```{r ttest, resize=TRUE}
tt.o = t.test(subset(df, group==1)$data, subset(df, group==2)$data)
tt.o %>% tidy %>% kable(format='latex')
```

Not significant, the p-value is `r tt.o$p.value`.


## Controlling for something

A linear model that controls for the `var` column.

```{r lm}
library(broom)
lm(group ~ data + var, data=df) %>% tidy %>% kable
```

Now it's significant, yeay !

## Third part

```{r graph}
library(ggplot2)
ggplot(df, aes(x=data, y=var, colour=factor(group))) + geom_point()
```
